{\Huge $ \ttlfnt{5e^{x+y}}$}: Searching over mathematical content in digital libraries

### 2015-02-01 jcdl2015/paper/main.tex

\begin{figure}
\centering
\begin{minipage}{.37\textwidth}
  \includegraphics[width=0.95\linewidth]{images/figures/input_interface.png}
  \captionof{figure}{Input interface.}
  \label{fig:test1}
\end{minipage}%
\end{figure}

\begin{figure}
\centering
\begin{minipage}{.37\textwidth}
  \includegraphics[width=0.95\linewidth]{images/figures/results_interface.png}
  \captionof{figure}{Result page.}
  \label{fig:test2}
\end{minipage}
\end{figure}

@@

In this demonstration, we focused on a limitation of CDS, and how our system, $5e^{x+y}$, provides efficient and precise searching capabilities over mathematical content. We presented our approach to model mathematical equations in terms of two different types of features. We extended the Lucene/Solr framework to handle specific type of content and through the Mathematica CAS we were able to include powerful functionalities such as pattern matching and equation simplificiation to our system, improving the quality of the results. Finally we presented our integration mechanism with the Invenio software through the solarpy library.

>>>>

\begin{figure}
\centering
\begin{minipage}{.27\textwidth}
  \includegraphics[width=0.9\linewidth]{images/figures/input_interface.png}
  \captionof{figure}{Input interface.}
  \label{fig:test1}
\end{minipage}%
\begin{minipage}{.27\textwidth}
  \includegraphics[width=0.9\linewidth]{images/figures/results_interface.png}
  \captionof{figure}{Result page.}
  \label{fig:test2}
\end{minipage}
\end{figure}

@@

In this demonstration, we focused on a a limitation of CDS, and how our system, $5e^{x+y}$, provides efficient and precise searching capabilities over mathematical content. We presented our approach to model mathematical equations in terms of two different types of features. We extended the Lucene/Solr framework to handle specific type of content and through the Mathematica CAS we were able to include powerful functionalities such as pattern matching and equation simplificiation to our system, improving the quality of the results. Finally we presented our integration mechanism with the Invenio software through the solarpy library.
